---
title: "index.rmd"
author: "sahirk"
date: "5/22/2022"
output: html_document
---

```{r setup, include=FALSE}
source("charts.R")
knitr::opts_chunk$set(echo = TRUE)
```

## Introductory Paragraph

We are interested in this domain because we all share a love for basketball and are curious about the statistics behind the professional level of one of our favorite games.
These datasets consist of data from 2018, 3 point percentages, and 2021-2022. 

## Summary Paragraph

Through the summary script, we were able to find out plenty of information. The highest 3 point percentage in the NBA during the 2021-2022 season was 1.0, the highest shooting distance average was 27.8 feet, and after some comparisons, we were able to find out that the shooting guard position (SG) takes the most 3pt attempts out of the top 50 attempts taken.

## Render the table

wfiqfiqbfibqf

## Chart purpose

```{r, echo=FALSE, warning=FALSE}
plot1
```

This plot shows the realtonship between Points earned per game vs a given position.
We can see some trends such as "PG-SG" and "SF-SG" earn almost no points as they
are defensive postions.

```{r, echo=FALSE, warning=FALSE}
plot2
```

Here we can see three throw count per game vs the the age of a player.
We can see overall ages 25-29 tend to make the most free throws per game.
Then there is a drastic fall at age 30

```{r, echo=FALSE, warning=FALSE}
plot3
```

In this plot we can see the relationship between Free throw count per game vs the 
amount of free throw attempts in a given game. This chart shows that there is hard to find a correlation between the success of free throws from a players age`