---
title: "index.rmd"
author: "sahirk"
date: "5/22/2022"
output: html_document
---

```{r setup, include=FALSE}
source("charts.R")
knitr::opts_chunk$set(echo = TRUE)
```

## Introductory Paragraph

kfnekfnwkfnkefk

## Summary Paragraph

dwnkfnknfwknkf

## Render the table

wfiqfiqbfibqf

## Chart purpose

```{r, echo=FALSE, warning=FALSE}
plot1
```

This plot shows the realtonship between Points earned per game vs a given position.
We can see some trends such as "PG-SG" and "SF-SG" earn almost no points as they
are defensive postions.

```{r, echo=FALSE, warning=FALSE}
plot2
```

Here we can see three throw count per game vs the the age of a player.
We can see overall ages 25-29 tend to make the most free throws per game.
Then there is a drastic fall at age 30

```{r, echo=FALSE, warning=FALSE}
plot3
```

In this plot we can see the relationship between Free throw count per game vs the 
amount of free throw attempts in a given game. This chart shows that there is hard to find a correlation between the success of free throws from a players age`